Solar jet observed at the limb in SDO/SST

### 2016-05-10 paper/ms_temp_paper.tex
Onset figure caption

multi.placement = 't'
multi.caption = "BIG CAPTION"
\end{pycode}

>>>>

multi.placement = 't'
multi.caption = "a) Observe the two bright points in the proximity of $()79, 60)$. We the point on the left is significatly brighter than the feinter on the right. We emphasise that the brightening around $(60, 50)$ is not a contributor to this jet. b) In this frame the brightpoints have extended, the feinter point has now extended up to $~95$ and the core of the brighter left feature has grown with it. c) At this point the two seperate points are now indistinguishable and the feature is now extending as one column. "
\end{pycode}
